\huge Simulation-based evaluation of susceptibility distortion correction methods in dMRI

### 2014-04-22 Publications/2013-ISBI14/poster/00-main.tex
Starting with poster...

% @Author: oesteban
% @Date:   2014-04-22 08:55:40
% @Last Modified by:   oesteban
% @Last Modified time: 2014-04-22 09:11:27

@@

\title{\huge Simulation-based evaluation of susceptibility distortion
  correction methods in diffusion MRI for connectivity analysis}
\author{Oscar Esteban$^{1,2,*}$, %
Alessandro Daducci$^{2}$, %
Emmanuel Caruyer$^{3}$, %
Kieran O'Brien$^{4}$,\\%
Mar\'ia J. Ledesma-Carbayo$^{1}$, %
Meritxell Bach-Cuadra$^{5,2}$, %
and Andr\'es Santos$^{1}$}%}
\institute[LTS5] {
$^{1}$Biomedical Image Technologies (BIT), ETSI Telecom.,
U. Polit\'ecnica de Madrid and CIBER-BBN, Spain. \\
$^{2}$Signal Processing Laboratory (LTS5), \'Ecole Polytechnique
F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland. \\
$^{3}$Section of Biomedical Image Analysis, Dpt. of Radiology,
University of Pennsylvania, Philadelphia, PA, USA. \\
$^{4}$Centre d'Imagerie Biom\'edicale (CIBM), and Dpt. of Radiology, University of Geneva, Geneva, Switzerland. \\
$^{5}$Radiology Department, CIBM, Lausanne University Hospital Center (CHUV)
and Lausanne University (UNIL), Switzerland.
$^{*}$Corresponding author (email: \texttt{oscar.esteban@upm.es})
}
\date[May 5th, 2012]{May 5th, 2012}

>>>>

% @Author: oesteban
% @Date:   2014-04-22 08:55:40
% @Last Modified by:   oesteban
% @Last Modified time: 2014-04-22 12:22:50

@@

\title{\huge Simulation-based evaluation of susceptibility distortion correction methods in dMRI}
\author[Esteban et al.]{O. Esteban$^{1,2}$\and%
A. Daducci$^{2}$\and%
E. Caruyer$^{3}$\and%
K. O'Brien$^{4}$\and%
MJ. Ledesma-Carbayo$^{1}$\and%
M. Bach-Cuadra$^{5,2}$\and%
A. Santos$^{1}$}%}
\institute{
$^{1}$~\includegraphics[height=2cm]{logos/BIT.pdf}~\includegraphics[height=2cm]{logos/UPM.pdf}\hfill%
$^{2}$~\includegraphics[height=2cm]{logos/LTS5.pdf}~\includegraphics[height=2cm]{logos/EPFL.pdf}\hfill%
$^{3}$~\includegraphics[height=2cm]{logos/SBIA.pdf}~\includegraphics[height=2cm]{logos/Penn.pdf}\hfill%
$^{4}$~\includegraphics[height=2cm]{logos/CIBM.pdf}~\includegraphics[height=2cm]{logos/UNIGE.pdf}\hfill%
$^{5}$~\includegraphics[height=2cm]{logos/CHUV.pdf}~\includegraphics[height=2cm]{logos/UNIL.pdf}%
}
\date[May 5th, 2012]{May 5th, 2012}
